---
title: "Logistic Regression Modeling (cleaned_12_Oct.csv)"
author: "Ziyan Zhao"
date: "07/10/2020"
output: pdf_document
header-includes: \usepackage{color,amsmath}
fontsize: 12pt
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lattice)
library(ggplot2)
library(caret)
```
### Attributes:
```{r setup, include=FALSE}
options(max.print=10000)
```

1: StageName	
\newline 2: RecordType.Name	
\newline 3: RICE_Supported__c	
\newline 4: Lead_Faculty__c	
\newline 5: Lead_School__c	
\newline 6: Parent_Opportunity__c	
\newline 7: Industry	
\newline 8: Industry_Sub_Type__c	
\newline 9: Business_Type__c	
\newline 10: Is_External__c	
\newline 11: ParentId	
\newline 12: tasks_events
\newline 13: CreatedYear	
\newline 14: CreatedMonth	
\newline 15: year_length	
\newline 16: oppo_busi	
\newline 17: fac_oppo	
\newline 18: oppo_Industry	
\newline 19: RN	
\newline 20: f_won_before

```{r echo=TRUE, message=FALSE, warning=FALSE, cache=TRUE}
# Reading Data In
data <- read.csv("/Users/ChantelleChiu/Documents/GitHub/Project-90106-G28/Chantelle/cleaned_12_Oct.csv",
                 header = TRUE, stringsAsFactors = T)
names(data) <- c("X1", "X2", "X3", "X4", "X5", "X6", "X7", "X8", "X9", "X10",
                 "X11", "X12", "X13", "X14", "X15","X16","X17","X18","X19","X20") 

summary(data)
```

Build regression model with 1 predictor ("StageName") and 19 features (X2-X20)
```{r echo=TRUE, message=FALSE, warning=FALSE, cache=TRUE}
# 10-fold cross_validation
train_control <- trainControl(method = "cv", number = 10)

# train the model on data set
model <- train(factor(X1)~X2+X3+X4+X5+factor(X6)+X7+X8+X9+factor(X10)+factor(X11)+factor(X12)+X13+X14+X15+X16+X17+X18+X19+factor(X20),
               data = data,
               trControl = train_control,
               method = "glm",
               family="binomial")
```


```{r echo=TRUE, message=FALSE, warning=FALSE, cache=TRUE, paged.print=TRUE}
summary(model)
```


```{r,echo=T, eval=T,cache=T, message=F,warning=F}
print(model)
```
```{r,echo=T, eval=T,cache=T, message=F,warning=F}
confusionMatrix(model)
```

Precision = 22.3/(15.1+22.3) = 59.63%

Recall = 22.3/(18.2+22.3) = 55.06%

```{r echo=TRUE, message=FALSE, warning=FALSE, cache=TRUE}
# train the model on data set
mod2 <- train(factor(X1)~X2+X3+X4+X5+factor(X6)+X7+X8+X9+factor(X10)+factor(X11)+factor(X12)+X13+X14,
               data = data,
               trControl = train_control,
               method = "glm",
               family="binomial")
```

```{r,echo=T, eval=T,cache=T, message=F,warning=F}
confusionMatrix(mod2)
```

```{r echo=TRUE, message=FALSE, warning=FALSE, cache=TRUE}
# train the model on data set
mod3 <- train(factor(X1)~X2+X3+X4+X5+factor(X6)+X7+X8+X9+factor(X10)+factor(X11)+factor(X12)+X13+X14+X15+X19+factor(X20),
               data = data,
               trControl = train_control,
               method = "glm",
               family="binomial")
```

```{r,echo=T, eval=T,cache=T, message=F,warning=F}
confusionMatrix(mod3)
```

```{r echo=TRUE, message=FALSE, warning=FALSE, cache=TRUE}
# train the model on data set
mod4 <- train(factor(X1)~X2+X3+X4+X5+factor(X6)+X7+X8+X9+factor(X10)+factor(X11)+factor(X12)+X13+X14+X16+X17+X18,
               data = data,
               trControl = train_control,
               method = "glm",
               family="binomial")
```

```{r,echo=T, eval=T,cache=T, message=F,warning=F}
confusionMatrix(mod4)
```

```{r echo=TRUE, message=FALSE, warning=FALSE, cache=TRUE}
# train the model on data set
mod5 <- train(factor(X1)~X2+X3+X4+X5+factor(X6)+X7+X8+X9+factor(X10)+factor(X11)+factor(X12)+X13+X14+X15+X16+X17+X18,
               data = data,
               trControl = train_control,
               method = "glm",
               family="binomial")
```

```{r,echo=T, eval=T,cache=T, message=F,warning=F}
confusionMatrix(mod5)
```