---
title: "Logistic Regression Modeling (cleaned_1-OCT-modelling.csv)"
author: "Ziyan Zhao"
date: "07/10/2020"
output: pdf_document
header-includes: \usepackage{color,amsmath}
fontsize: 12pt
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lattice)
library(ggplot2)
library(caret)
```
### Attributes:
1: StageName (factor)	
2: RecordType.Name
3: RICE_Supported__c
\newline 4: CreatedDate
\newline 5: Actual_Close_Date__c (factor)
\newline 6: Lead_Faculty__c
\newline 7: Lead_School__c
\newline 8: Parent_Opportunity__c (factor)
\newline 9: RecordType.Name.1
\newline 10: Industry
\newline 11: Industry_Sub_Type__c	
\newline 12: Business_Type__c
\newline 13: Is_External__c (facotr)
\newline 14: ParentId (factor) 
\newline 15: CreatedYear
\newline 16: CreatedMonth

```{r,echo=T, eval=T,cache=T, message=F,warning=F}
# Reading Data In
data <- read.csv("/Users/ChantelleChiu/Documents/GitHub/Project-90106-G28/Chantelle/cleaned_1-OCT-modelling.csv",
                 header = TRUE, stringsAsFactors = T)
names(data) <- c("X1", "X2", "X3", "X4", "X5", "X6", "X7", "X8", "X9", "X10",
                 "X11", "X12", "X13", "X14", "X15","X16") 


summary(data)
```

Build regression model with 1 predictor ("StageName") and 15 features (X2-X16)
```{r,echo=T, eval=T,cache=T, message=F,warning=F}
# 10-fold cross_validation
train_control <- trainControl(method = "cv", number = 10)

# train the model on data set
model <- train(factor(X1)~X2+X3+X4+factor(X5)+X6+X7+factor(X8)+X9+X10+X11+X12+factor(X13)+factor(X14)+X15+X16,
               data = data,
               trControl = train_control,
               method = "glm",
               family="binomial")
```

